Model LF

### 2022-12-21 paper version 2.Rmd
Commit

plot((i_g_01 - i_g_bs1), col= "red")

@@

plot(nsben_h_01 - nsben_h_bs1, col= "red")

@@

par(mfrow=c(1,2))
plot(((yk_ds_01 - yk_ds_bs1) / yk_ds_bs1)*100, col= "blue", xlab= "Year", ylab= "% Change in GDP", main= "GDP", ylim= c(-0.13, 0.06));
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2)*100, col= "green");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3)*100, col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green","red"));
grid()

plot(((nl_g_01 - nl_g_bs1)), col= "blue", xlab= "Year", ylab= "Change in Government net lending", main= "Change in Government net-lending", ylim= c(-500, 2500));
lines(((nl_g_02 - nl_g_bs2)), col= "green");
lines(((nl_g_03 - nl_g_bs3)), col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green","red"));
grid()
```

```{r}
plot(((unemp_01 - unemp_bs1)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Unemployment", ylim= c(-300,3000));
lines(((unemp_02 - unemp_bs2)*1000), col= "green");
lines(((unemp_03 - unemp_bs3)*1000 ), col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "green", "red"));
grid()

plot(((nben_h_un_01 - nben_h_un_bs1)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Unemployment");
lines(((nben_h_un_02 - nben_h_un_bs2)*1000), col= "green");
lines(((nben_h_un_03 - nben_h_un_bs3)*1000 ), col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "green", "red"));
grid()
```

>>>>

@@

@@

par(mfrow=c(1,2))
plot(((yk_ds_01 - yk_ds_bs1) / yk_ds_bs1)*100, col= "blue", xlab= "Year", ylab= "% Change in GDP", main= "GDP", ylim= c(-0.05, 0.05));
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2)*100, col= "green");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3)*100, col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green","red"));
grid()

plot(((nl_g_01 - nl_g_bs1)), col= "blue", xlab= "Year", ylab= "Change in Government net lending", main= "Change in Government net-lending", ylim= c(-400, 500));
lines(((nl_g_02 - nl_g_bs2)), col= "green");
lines(((nl_g_03 - nl_g_bs3)), col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green","red"));
grid()
```

```{r}
plot(((unemp_01 - unemp_bs1)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Unemployment", ylim= c(-300,1000));
lines(((unemp_02 - unemp_bs2)*1000), col= "green");
lines(((unemp_03 - unemp_bs3)*1000 ), col= "red");
legend("left", legend=c("Scenario 1","Scenario 2", "Scenario 3"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "green", "red"));
grid()
